Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-04-12 paper/AlignedIsotropicGW.tex
Removing a bit of red.
Fix #10, effect of other parameters on chi_eff measurements.

\newcommand{\OOneSigmaIsoAligned}{\checkme{1.7}}
\newcommand{\OOneOddsIsoAligned}{\checkme{0.087}}
\newcommand{\OTwoSigmaIsoAlignedMin}{\checkme{2.9}}
\newcommand{\OTwoOddsIsoAlignedMin}{\checkme{0.0035}}

@@

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next two years
\citep{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming 10
additional detections with similar observational uncertainties
\ilya{[I think it would be useful to specify (in an appendix?) what
  model we use for the observational uncertainty on $\chieff$.]}
drawn from each of our six zero-parameter models for the spin
distribution in addition to the three existing detections from
O1, we find the odds ratios shown in Figure
\ref{fig:O2-predictions}.  We find that most scenarios with an
additional 10 detections allow the simulated angular distribution to
be inferred with greater than $5\sigma$ ($2.9 \times 10^{-7}$ odds)
credibility; and in the most pessimistic case the distinction is
typically $\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$
odds ratio).  While such future detections should permit a confident
distinction between \emph{angular} distributions, we would remain much
less certain about the \emph{magnitude} distribution among the three
options considered here until we have a larger number of observations.
In Figure \ref{fig:O2-predictions}, the odds ratio between different
magnitude distributions with the same angular distribution is much
closer to unity than the odds ratio between angular distributions.

>>>>

\newcommand{\OOneSigmaIsoAligned}{1.7}
\newcommand{\OOneOddsIsoAligned}{0.087}
\newcommand{\OTwoSigmaIsoAlignedMin}{2.9}
\newcommand{\OTwoOddsIsoAlignedMin}{0.0035}

@@

Estimates of the rate of \ac{BBH} coalescences give a reasonable
chance of 10 additional \ac{BBH} detections in the next two years
\citep{O1-BBH,2016ApJ...833L...1A,2016ApJS..227...14A}.  Assuming 10
additional detections drawn from each of our six zero-parameter models
for the spin distribution in addition to the three existing detections
from O1, with observational uncertainties drawn randomly from the
three Gaussian widths used to approximate the $\chieff$ posteriors in
Figure \ref{fig:O1-posteriors}\footnote{The measurement uncertainty in
  $\chieff$ depends on the other parameters of the merging \ac{BBH}
  system, particularly on the mass ratio.  Our assumption about future
  observational uncertainties is appropriate if the parameters of the
  existing three events are representative of the parameters of future
  detections.}, we find the odds ratios shown in Figure
\ref{fig:O2-predictions}.  We find that most scenarios with an
additional 10 detections allow the simulated angular distribution to
be inferred with greater than $5\sigma$ ($2.9 \times 10^{-7}$ odds)
credibility; and in the most pessimistic case the distinction is
typically $\OTwoSigmaIsoAlignedMin\sigma$ ($\OTwoOddsIsoAlignedMin$
odds ratio).  While such future detections should permit a confident
distinction between \emph{angular} distributions, we would remain much
less certain about the \emph{magnitude} distribution among the three
options considered here until we have a larger number of observations.
In Figure \ref{fig:O2-predictions}, the odds ratio between different
magnitude distributions with the same angular distribution is much
closer to unity than the odds ratio between angular distributions.
